|

### 2024-11-17 doc/paper.qmd
Abstract update

---
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group - Assignment III\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging Worldscope data on financial information, this repository showcases a reproducible workflow that integrates Python scripts for data analysis. The project’s output demonstrates a comprehensive application of skills to replicate and extend the findings from the seminal paper by Leuz, Nanda, and Wysocki (2003), particularly in providing descriptive statistics for four individual earnings management measures, as well as an aggregate earnings management score across various countries. In doing so, it documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and how to structure a reproducible empirical research project.
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

>>>>

---
title: |
  | Audit market concentration in the EU:
  | Corporate Decision-Making and Quantitative Analysis - Assignment I\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging Audit Analytics database on Transparency Report data, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization. The project replicates and extends findings from the European Commission’s 2024 report by analyzing and visualizing audit firms’ Big 4, CR4, and 10KAP  market shares in the number of PIE statutory audits for 2021 across EU countries and at the EU level. The results include a detailed breakdown of market concentration trends, offering insights into the dominance of major audit firms across different jurisdictions. In doing so, it documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and how to structure a reproducible empirical research project.
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---
